Implicit yaddayadda

### 2011-10-28 papers/PLDI2012/implicitization.tex
workarounds

In cases where the formula is expressed in too rich a logic for the SMT-solver to deal with, a number of workarounds are possible:
\begin{itemize}[itemsep=-\parsep,topsep=0pt,partopsep=0pt]
\item \emph{Linearization}, as per \citet{DBLP:conf/vmcai/Mine06}, which overapproximates nonlinear semantics by linear semantics. However, such transformations are not implemented in our tool.
\item Replacing the results of nonlinear operations by ``unknown''.
\end{itemize}

>>>>

In cases where the formula is expressed in too rich a logic for the SMT-solver to deal with, a number of workarounds are possible, including:
(i) \emph{Linearization}, as per \citet{DBLP:conf/vmcai/Mine06}, which overapproximates nonlinear semantics by linear semantics.
(ii) Replacing the results of nonlinear operations by ``unknown''.
Neither is currently implemented in our tool.
